Age-related changes in plant growth and traits

### 2015-12-09 Flowering_parts_charts.Rmd
looking at data - mostly thinking about accessory costs, seed set

labels.barplot <- function(x=NULL){
  names(col.barplot(x))
}

Invest2 <- merge(InvestmentByPart,select(accessoryList,-sort), by=c("species","part"))

for(v in c("weight")) {
  i <- is.na(Invest2[[v]])
  Invest2[[v]][i] <- 0
}
```
View(Invest2)

@@

@@

@@

pdf("figs2/Flower_parts_fewer.pdf", height=11, width=8)
plot
par(mfrow=c(2,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(.5,.5,.5,.5)) 
for(spp in names(data)) {
  pie(data[[spp]]$weight,labels=data[[spp]]$labels,main=spp,col=col.barplot(data[[spp]]$parts_fewer_yet),cex=0.8)
}
#dev.off()
```

>>>>

col.accessory <- function(x=NULL){
  ret <- c("firebrick1","firebrick","deepskyblue1","deepskyblue3","deepskyblue4")
  names(ret) <- c("prepollination_abort","prepollination_success","postpollination_abort","packaging_dispersal","propagule")

labels.barplot <- function(x=NULL){
  names(col.barplot(x))
}
```

Invest2 for accessory part
``` {r}
Invest2 <- merge(InvestmentByPart,select(accessoryList,-sort), by=c("species","part"))

for(v in c("weight")) {
  i <- is.na(Invest2[[v]])
  Invest2[[v]][i] <- 0
}
```

names(Invest2)

@@

by "accessory_part"
```{r}
SummaryInvest <- 
  Invest2 %>%
  group_by(accessory_part,species) %>%
  summarise_each(funs(sum),weight)

@@

#barplot by accessory grouping
```{r}
barplot_data <- select(SummaryInvest,species, accessory_part, prop_weight)
barplot_data <- spread(barplot_data,species,prop_weight,fill=0,drop=FALSE)
barplot_data <- barplot_data[order(factor(barplot_data$accessory_part,levels=c(c(
  "prepollination_abort","prepollination_success","postpollination_abort","packaging_dispersal","propagule")))),]

#pdf("figs2/Flower_parts_barchart.pdf", height=8, width=11)
#plot
#win.metafile("figs2/RA_talk_barplot.wmf", height=4, width=10)
#plot
par(mfcol=c(1,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)) 
midpoints <- barplot(barplot_data_matrix,beside=FALSE,width=0.8,cex.axis=.7,cex.names=.7,xlim=c(.5,17.2),col=col.accessory(barplot_data$accessory_part),ylab="proportion repro investment")
legend(13.5,1,legend=barplot_data$accessory_part,pch=16, cex=1,bty="n",col=col.accessory(barplot_data$accessory_part))

#text(midpoints,(barplot_data_matrix), labels=barplot_data_matrix)
#dev.off()
```

@@

#pdf("figs2/Flower_parts_fewer.pdf", height=11, width=8)
plot
par(mfrow=c(4,4), cex=1, omi=c(.1,.1,.1,.1), mai=c(.5,.5,.5,.5)) 
for(spp in names(data)) {
  pie(data[[spp]]$weight,labels=data[[spp]]$accessory_part,main=spp,col=col.accessory(data[[spp]]$accessory_part),cex=0.8)
}
#dev.off()
```
